Enhancing Accelerometer-based Activity Recognition with Capacitive Proximity Sensing

### 2012-08-24 Paper/Paper.tex
final camera ready version

\begin{figure}[!t]
	\centering
		\includegraphics[width=\textwidth]{../Auswertung/images/tobias_4.pdf}
	\caption{An example of the ``getting things'' activity, where the participants had to get food and dishes from shelves and lockers. The proximity sensor peaks in the beginning (9s and 19s) indicate immediate proximity to shelf, and to the locker (55-63s) in the kitchen (upper plot). The signal drop at the end results from the participant placing his hand on the table when she was finished.}
	\label{fig:get_things}
\end{figure}

@@

\begin{figure}[t]
	\centering
		\includegraphics[width=1.00\textwidth]{../Auswertung/images/eugen_9.pdf}
	\caption{During the sleeping activity the data from both sensors remains constant for large time spans. The capacitive sensor shows the coverage of the arm with either cushions, blankets or the proximity to the mattress, the head or body of the participant.}
	\label{fig:sleeping}
\end{figure}

The sleeping activity (an example shown in Figure \ref{fig:sleeping}) was classified with an average F-measure of 83.2\%, which increased to 86.9\% when using the proximity data. In this case, the capacitive proximity sensor is able to capture the surrounding cushions and blankets, as well as the body or head of the participant. The accelerometer data and the proximity data have larger periods of low variance, which is a cause for confusion with the ``lying on the couch'' activity.

@@

We would like to thank our evaluation participants from TU Darmstadt and Fraunhofer IGD.

>>>>

\begin{figure}[t]
	\centering
		\includegraphics[width=\textwidth]{../Auswertung/images/tobias_4.pdf}
	\caption{An example of the ``get things'' activity, where the participants had to get food and dishes from shelves and lockers. The proximity sensor peaks in the beginning (9s and 19s) indicate immediate proximity to shelf, and to the locker (55-63s) in the kitchen (upper plot). The signal drop at the end results from the participant placing his hand on the table when she was finished.}
	\label{fig:get_things}
\end{figure}

@@

\begin{figure}[t]
	\centering
		\includegraphics[width=1.00\textwidth]{../Auswertung/images/eugen_9.pdf}
	\caption{During the sleeping activity the data from both sensors remains constant for large time spans. The capacitive sensor plot shows the coverage of the arm with either cushions, blankets or the proximity to the mattress, other parts of the bed, the head or body of the participant.}
	\label{fig:sleeping}
\end{figure}

The sleeping activity (an example shown in Figure \ref{fig:sleeping}) was classified with an average F-measure of 83.2\%, which increased to 86.9\% when using the proximity data. In this case, the capacitive proximity sensor is able to capture the surrounding cushions and blankets, as well as the body or head of the participant. The accelerometer data and the capacitive proximity data have larger periods of low variance, which is a cause for confusion with the ``lying on the couch'' activity.

@@

We would like to thank our evaluation participants from the Technische Universit\"at Darmstadt and Fraunhofer IGD.
